---
title: CV - Dingrui(Frank)
author: Dingrui(Frank) Zhang
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/custom_resume.css', 'css/styles_html.css', 'resume']
    # css: ['css/custom_resume.css', 'css/styles_pdf.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
params:
  doctype: "HTML" # "PDF" or "HTML" is automatically updated in update_resume.R 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

#load packages
library(tidyverse)
library(readxl)
library(glue)

#source helper functions
source('helper_functions.R')


# get data from xlsx file
position_data <- readxl::read_excel('resume_data.xlsx', 
                                    sheet = "positions", 
                                    na = c("", "NA", "na")) 

skill_data <- readxl::read_excel('resume_data.xlsx', 
                                 sheet = "skills",
                                 na = c("", "NA", "na"))                                 
```


Aside
================================================================================


Contact {#contact}
--------------------------------------------------------------------------------


- <i class="fa fa-map-marked-alt"></i> Frank Zhang
- <i class="fa fa-phone"></i> +61 0414-350-521
- <i class="fa fa-envelope"></i> zhang@ding-rui.com
- <i class="fa fa-github"></i> [github.com/frankzhangsyd](https://github.com/frankzhangsyd)
- <i class="fab fa-linkedin-in"></i> [Dingrui(Frank) Zhang](https://www.linkedin.com/in/dingrui-zhang/)
- <i class="fas fa-home"></i> [ding-rui.org](https://www.ding-rui.org/)


```{r download, echo=FALSE}
# if doctype is html add link to download a pdf version
if(params$doctype == "HTML"){
  cat("[<i class='fas fa-download'></i> Download as a PDF](https://github.com/frankzhangsyd/vitae/raw/master/output/Frank-Zhang-CV.pdf)")
}

```



<br>


Coding {#coding}
--------------------------------------------------------------------------------

```{r coding, dev.args=list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "coding")

```

<br>

Visualization {#Visualization}
--------------------------------------------------------------------------------

```{r visualization, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "visuals")

```

<br>

Strength {#Strength}
--------------------------------------------------------------------------------

```{r strength, dev.args = list(bg = 'transparent')}

# function from helper_functions.R
build_skill_bars(skill_data, "software")

```

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made w/ [**pagedown**](https://github.com/rstudio/pagedown).   
Source code: [**Github repo**](https://github.com/frankzhangsyd/vitae).

Last updated on `r Sys.Date()`.
<br>
<br>


Main
================================================================================


Dingrui(Frank) Zhang {#title}
--------------------------------------------------------------------------------

### Business Analyst  |  R Developer

I enjoy working with data to solve business problems and build tools that help
people. My favorite part of working in data science is the constant opportunity 
to learn, from statistics to real business problems.



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r education}
print_section(position_data, 'education')
```



Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

```{r jobs}
print_section(position_data, 'work')
```



<i class="fas fa-rocket"></i> Professional Development
--------------------------------------------------------------------------------

```{r development}
print_section(position_data, 'development')
```
